Ecosystem size and complexity are extrinsic drivers of food chain length in branching networks

### 2022-05-10 rmd/suppl_info.Rmd
Update suppl_info.Rmd

  table_legend <- paste0("Sensitivity analysis of the ", c_text[i]," effect on food chain length. Parameter estimates of linear regression models are shown. The response variable is the Spearman's rank correlation between food chain length and ", c_text[i],". Response and explanatory variables (i.e., simulation parameters) were standardized (mean = 0, SD = 1) before the analysis.")

  knit_chunk <- paste0("## Table S", i + j, " Sensitivity analysis for ", c_text[i]," \n",
                       table_legend,
                       "\n```{r table_s", i + j,", results='asis'}
                       \n\n
                       table_stvy[[", i,"]]
                       \n\n
                       ```\n",
                       "\n\\pagebreak\n")

@@

  knit_chunk <- paste0("## Figure S", K * (i - 1) + k + j, " ", str_to_sentence(c_text[i]), " effect on food chain length", " \n",
                       "\n```{r figure_s", K * (i - 1) + k + j,", fig.height = 10, fig.width = 11.5}
                       \n\n
                       list_g_fcl[[", i, "]][[", k, "]]
                       \n\n
                       ```\n",
                       figure_legend,
                       "\n\\pagebreak\n")

>>>>

  table_legend <- paste0("Sensitivity analysis of the ", c_text[i]," effect on food chain length. Parameter estimates of linear regression models are shown. The response variable is the Spearman's rank correlation between food chain length and ", c_text[i],". Response and explanatory variables (i.e., simulation parameters) were standardized (mean = 0, SD = 1) before the analysis.\n")

  knit_chunk <- paste0("## Table S", i + j, " Sensitivity analysis for ", c_text[i],
                       "\n\n",
                       table_legend,
                       "```{r table_s", i + j,", results='asis'}
                       \n\n
                       table_stvy[[", i,"]]
                       \n\n",
                       "```",
                       "\n\\pagebreak\n")

@@

  knit_chunk <- paste0("## Figure S", K * (i - 1) + k + j, " ", str_to_sentence(c_text[i]), " effect on food chain length",
                       "\n\n",
                       "```{r figure_s", K * (i - 1) + k + j,", fig.height = 10, fig.width = 11.5}",
                       "\n\n
                       list_g_fcl[[", i, "]][[", k, "]]
                       \n\n",
                       "```",
                       "\n\n",
                       figure_legend,
                       "\n\\pagebreak\n")
